  ---
title: "Does Price of House vary based on the City"
author: "Gobind Agarwal"
date: "20 December"
output:
  html_document:
    number_sections: yes
  
---
Null Hypothesis:-Price of House varies with City
Alternative Hypothesis :- Price of House does not varies with City

```{r}
setwd("/home/msc1/R/Assignment 2")
getwd()
```

# Load data and see the structure of data
Head will show first 6 rows of the data set

```{r}
HousePrice<-read.csv("HousePrices_HalfMil.csv",header=TRUE)
head(HousePrice)
str(HousePrice)
```

# Check  Missing values
```{r}
colSums(is.na(HousePrice))
```
There is no missing Value in the dataset

#Correaltional Plot of the Dataset
```{r}
ncol(HousePrice)
cor(HousePrice[1:16])
library(corrplot)
corrplot(cor(HousePrice[1:16]), order="hclust",tl.col="black",tl.cex=.75)
```


It is clearly seen from the correlational plot that Price and city is having some positive correaltion

#Descriptive Statistics 
##Box Plot
```{r}
attach(HousePrice)
boxplot(Prices~City , col=c("Green","Orange","Red"))
```
Means are not same with respect to city

#CLT
Through Central limit theorem we can say, because the number of data points is more than 30 (5,00,000) , the datasets follows a Normal Distribution

#Test For Normality
##These Test are done to check that dataset is Normal or not

Null Hypothesis : Distribution is Normal

Alternative Hypothesis : Distribution is not Normal

###Shapiro Test
Sample of 5000 from whole dataset is taken for the test

Area,Prices,City
```{r}
#shapiro.test(HousePrice$Area)
Area_check<-sample(HousePrice$Area,5000)
shapiro.test(Area_check)
Prices_check<-sample(HousePrice$Prices,5000)
shapiro.test(Prices_check)
City_check<-sample(HousePrice$City,5000)
shapiro.test(City_check)

```
P-Values  Are Close to 0 , therefore Reject Null Hypothesis

###QQ PLOT
```{r}
qqnorm(Area_check)
qqnorm(Prices_check)
qqnorm(City_check)

```
Plot shows that distribution is not normal

###Normality Tester through Library BSDA
Center plot is the given data. 
Randomly generated normally distributed data is plotted on all sides of it. 
Red Means it is not Normally Distributed.
```{r}
library(BSDA)
ntester(Area_check)
ntester(Prices_check)
ntester(City_check)
```


After doing all the Test, it can be concluded that the given Dataset is NOT NORMAL


# Homegeneous Variance Test
To Test that the variance across the group is same or not

Homoscadasticity Or Heteroscadasticity is seen

##Bartlett Test

Null Hypothesis : Variance across the group is same.

```{r}
bartlett.test(HousePrice[,1],HousePrice[,9])
```
Area And City - Same Variance
```{r}
bartlett.test(HousePrice[,8],HousePrice[,3])
```
FirePlace and Floor - Same Variance
```{r}
bartlett.test(HousePrice[,6],HousePrice[,12])
```
Black Marble and Fiber - Same Variance
```{r}
bartlett.test(HousePrice[,16]~HousePrice[,9])
```
p-value is greater than 0.05(alpha level)

ACCEPT NULL HYPOTHESIS : Prices varies with City

#Anova Test
This is done to analyse the variance of the dataset.

City is taken as factor.

```{r}
attach(HousePrice)
city_factor<-as.factor(City)
aov_1 <- aov(Prices~city_factor)
summary(aov_1)
```
Summary Shows P-Values is close to 0 (<0.05) therefore there is a variation between city and prices

# Differences between the Mean level of City
95% confidence level
It shows the difference between two cities
```{r}
HSDTEST<-TukeyHSD(aov_1)
HSDTEST
plot(HSDTEST)
model.tables(aov_1,"effects")
model.tables(aov_1,"means")
```
We observe that there is a lot of difference between first city and third city.


#Linear Regression
Area= B0 + Garage(B1) + FirePlace(B2) + Baths(B3) + White.Marble(B4) + Black.Marble(B5) + Floors(B6) + Solar(B7) + Electric(B8) + Fiber(B9) + Glass.Doors(B10) + Swiming.Pool(B12) + Garden(B13)

```{r}
attach(HousePrice)
model_area <- lm(Area~Garage+FirePlace+Baths+White.Marble+Black.Marble+Floors+Solar+Electric+Fiber+Glass.Doors+Swiming.Pool+Garden,data=HousePrice)
summary(model_area)
```
Observation :- P-Values (other than B0) is more than 0.05. 
So These factor are affecting the area of a House

Checking whether How area is affecting city. 

City= B0 + Area(B1)
```{r}
model_city <- lm(City~Area,data=HousePrice)
summary(model_city)
```



Checking whether How Price is affected by Area or by City

```{r}
model_Price_1 <- lm(Prices~Area,data=HousePrice)

summary(model_Price_1)
```

```{r}
model_Price_2 <- lm(Prices~City,data=HousePrice)
summary(model_Price_2)
```




#CONCLUSION :- 

-Dataset is not normally distributed.

-Variance between price and city is not same.

-TukeyHSD shows the difference beteen cities prices are significant.

-Prices varies with respect to City
